
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Group: Adam, Sam, Will

## Introduction 

In this notebook, we are reverse engineering the story, "Comic Books are still Made by Men, for Men and About Men" (https://fivethirtyeight.com/features/women-in-comic-books/)

## Load libraries

Loading required libraries for this analysis.

```{r}
options(scipen=999)
library(tidyverse)
library(janitor)
library(lubridate)

```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data. 

```{r}
#Load DC Comics Data
dc_data <- read_csv("dc-wikia-data.csv")

#Load Marvel Comics Data
marvel_data <- read_csv("marvel-wikia-data.csv")
```

## Data Dictionary:
*page_id*: The unique numeric code given to each character page in the Wikia database.
*name*: The character's name from the comics; it can include the character's superhero name, real name, and universe/reality of origin within the comics.
*urlslug*: The character's slug at the end of the Wikia (now Fandom) URL on their website.
*ID*: Whether a given character has a secret or public identity within the comics, or no dual identity at all.
*ALIGN*: Whether the character is known as a good, bad or nuetral character within the comics.
*EYE*: The character's eye color.
*HAIR*: The character's hair color.
*SEX*: The character's gender identity/sex, depending on the character.
*GSM*: If a character is part of the LGBTQ+ community, a value indicates what queer identity the character has.
*ALIVE*: Whether a character is currently alive within the comic's continuity.
*APPEARANCES*: How many individual comic issues the character has appeared in.
*FIRST APPEARANCE*: The month and year of the character's first appearance.
*Year*: The year of the character's first appearance.

## Data Explanation:
This story's data was sourced from Wikia, now known as Fandom, a fan-driven database that works as a living encyclopedia for multiple properties within popular culture, including Marvel and DC. Because the Wikias work similar to Wikipedia, with multiple decentralized writers and editors, information is often mutable and ever-changing. The data for this story was likely inaccurate/dated by the time of the story's publishing in 2014. Today, it's even more out of date. It's worth noting that within the world of comics, nothing is permanent: eye and hair colors change with iterations and illustrators over decades, and characters die and resurrect on a regular basis. Secret identities are kept and revealed, and the data never remains stagnent. Despite these caveats and limitations, the story's writer, Walt Hickey, acknowledges that DC and Marvel themselves have no public-facing databases for their characters. Because of this, the Wikia was his best and most reliable source, even if inaccuracies exist. Although the Marvel and DC dataframes are taken from different Wikias, the variables are the same, which allows accurate comparisons between them.

## Sentences to Engineer
In this notebook, we are reverse engineering five sentences from the story.

Finding #1:

"Women and men were almost exactly equally likely to have a secret identity in the Marvel universe (49.4 percent of males and 49.5 percent of females), while in the DC universe 51 percent of males had a secret identity and 45 percent of females did. While it’s not a perfect stand-in, we can also infer that men may be slightly more likely to be superheroes or villains — rather than just normal, unpowered side characters — than women in the DC universe."

Analysis: After removing na values in multiple related categories, including appearances, we completed a simple calculation to find that the Marvel characters, both male and female, have secret identities at a rate of just above 49 percent, while DC male characters are secretive at 50.92 percent and DC female characters are secretive at 44.96 percent. After rounding, these findings exactly replicate the findings of the original article. 
gggfrrrrrrr
```{r}
# Filter to characters with at least one appearance and known gender and alignment. We're only looking for male or female characters, so we'll filter out the rest here too.
marvel_id <- marvel_data |>
  filter(!is.na(ID)) |>
  filter(!is.na(APPEARANCES)) |>
  filter(!is.na(SEX)) |>
  filter(SEX == "Female Characters" | SEX == "Male Characters")
dc_id <- dc_data |> 
  filter(!is.na(ID)) |>
  filter(!is.na(APPEARANCES)) |>
  filter(!is.na(SEX)) |>
  filter(SEX == "Female Characters" | SEX == "Male Characters")

#Sort by Gender and count by ID, then calculate percentage
marvel_id |>
  group_by(SEX, ID) |>
  summarise(count = n()) |>
  group_by(SEX) |>
  mutate(
    total_gender = sum(count),
    percent_gender = count / total_gender * 100
  )

dc_id |>
  group_by(SEX, ID) |>
  summarise(count = n()) |>
  group_by(SEX) |>
  mutate(
    total_gender = sum(count),
    percent_gender = count / total_gender * 100
  )
```

Finding #2:

"Women were substantially underrepresented among characters with at least one appearance. Among the characters for which we have gender data, females made up only 29.3 percent of the DC character list and 24.7 percent of the Marvel roster."

Analysis: After removing na values, we completed a simple calculation to find that the DC percentage was 24.749, and the Marvel percentage was 29.25159. After rounding, these findings exactly replicate the findings of the original article. 

```{r}
# Filter to characters with at least one appearance and known gender
marvel_gender <- marvel_data |>
  filter(!is.na(APPEARANCES), !is.na(SEX)) 

dc_gender <- dc_data |>
  filter(!is.na(APPEARANCES), !is.na(SEX)) 

# Calculate percent female
marvel_gender |>
  summarize(marvel_percent_female = mean(SEX == "Female Characters") * 100) |>
  arrange()

dc_gender |>
  summarize(dc_percent_female = mean(SEX == "Female Characters") * 100) |>
  arrange()
```

Finding #3:

"The same trend bears out when we look at characters with higher appearance counts. When we zero in on the 2,415 DC and 3,342 Marvel characters with gender data who appear at least 10 times — the set of characters that probably gives the most consistent view of what we see on the page — female characters make up only 30.9 percent of the DC universe and 30.6 percent of the Marvel universe."

Analysis: Similar to the last finding, we removed na values and created a new dataset for characters with more than or equal to 10 appearances, then replicated the same calculations to find that the DC percentage was 30.93043 and the Marvel percentage was 30.62843. After rounding, these findings exactly replicate the findings of the original article. 

```{r}
# Filter to characters with at least 10 appearances and known gender
marvel_10 <- marvel_data |>
  filter(!is.na(APPEARANCES), !is.na(SEX), APPEARANCES >= 10)

dc_10 <- dc_data |>
  filter(!is.na(APPEARANCES), !is.na(SEX), APPEARANCES >= 10)

# Calculate percent female among those
marvel_10 |>
  summarize(marvel_10_percent_female = mean(SEX == "Female Characters") * 100) |>
  arrange()

dc_10 |>
  summarize(dc_10_percent_female = mean(SEX == "Female Characters") * 100) |>
  arrange()

```

Finding #4:

"When we focus on only the most frequently appearing characters in each universe — the stars of the show — the data changes. Of characters with gender data and 100 or more appearances (294 DC characters and 414 Marvel characters), only 29.0 percent of DC’s are female, and a similar 31.1 percent of the Marvel crowd is."

Analysis: This method is virtually the same as the previous one with appearances filtered to 100 versus just 10. The significance of the distinct groups is that this represents characters that were relatively successful and popular. Rounded to the tenth, the findings produced here match those of the article. 

```{r}
# Filter to characters with at least 100 appearances and known gender
marvel_100 <- marvel_data |>
  filter(!is.na(APPEARANCES), !is.na(SEX), APPEARANCES >= 100)

dc_100 <- dc_data |>
  filter(!is.na(APPEARANCES), !is.na(SEX), APPEARANCES >= 100)

# Calculate percent female among those
marvel_100 |>
  summarize(marvel_100_percent_female = mean(SEX == "Female Characters") * 100) |>
  arrange()

dc_100 |>
  summarize(dc_100_percent_female = mean(SEX == "Female Characters") * 100) |>
  arrange()

```

Finding #5:

"In both DC and Marvel, women were of neutral allegiance at a higher rate than men. Men were also more likely to be bad in each universe — in fact, bad-aligned men alone outnumbered all women combined. In other words, there’s something of a paucity of female villains.”

Analysis: We're creating new datasets and filtering na values of our relevant fields, SEX and ALIGN. For each universe, we summarised counts for both of those fields, and then grouped by only SEX to create new fields that show us the proportion of each gender that is good bad or neutral. The findings above can all be observed in the results below.  

```{r}
#Filter to rows with values for alignment and sex, get totals for each combination
marvel_alignment <- marvel_data |>
  filter(!is.na(ALIGN), !is.na(SEX)) |>
  group_by(SEX, ALIGN) |>
  summarise(count = n()) |>
  group_by(SEX) |>
  mutate(
    total_gender = sum(count),
    percent_gender = count / total_gender * 100
  )

dc_alignment <- dc_data |>
  filter(!is.na(ALIGN), !is.na(SEX)) |>
  group_by(SEX, ALIGN) |>
  summarise(count = n()) |>
  group_by(SEX) |>
  mutate(
    total_gender = sum(count),
    percent_gender = count / total_gender * 100
  )

#Return tables
marvel_alignment

dc_alignment

```


